An Elaboration on\\Order-Adaptive Regularisation for Variational Optical Flow:\\Global, Local and in Between

### 2018-08-09 seminar_vof/paper/paper.tex
written abstract and filled in citations

%% Abstract section.
\abstract{%
  Hier sollte eine kurze Zusammenfassung der Ausarbeitung stehen. Der
  Umfang sollte 150 bis 250 Worte betragen. Duis autem vel eum iriure
  dolor in hendrerit in vulputate velit esse molestie consequat, vel
  illum dolore eu feugiat nulla facilisis at vero eros et accumsan et
  iusto odio dignissim qui blandit praesent luptatum zzril delenit
  augue duis dolore te feugait nulla facilisi. Lorem ipsum dolor sit
  amet, consectetuer adipiscing elit, sed diam nonummy nibh euismod
  tincidunt ut laoreet dolore magna aliquam erat volutpat.

  Ut wisi enim ad minim veniam, quis nostrud exerci tation ullamcorper
  suscipit lobortis nisl ut aliquip ex ea commodo consequat. Duis
  autem vel eum iriure dolor in hendrerit in vulputate velit esse
  molestie consequat, vel illum dolore eu feugiat nulla facilisis at
  vero eros et accumsan et iusto odio dignissim qui blandit praesent
  luptatum zzril delenit augue duis dolore te feugait nulla facilisi.
} % end of abstract

@@

In computer vision, the field of optic flow deals with the estimation of a 2-dimensional flow field based on two consecutive frames of an image sequence.
\\(mehr dazu warum optic flow geil ist)\\
Different methods for flow estimation exist, such as ... ... and variational optic flow which is based on the calculus of variations.
In the following the concept of variational flow estimation is recapitulated and the approach by Maurer, Stoll and Bruhn \cite{daspaper} with order adaptive regulalarization is presented.

@@

Unfortunately this sophisticated scheme comes at a larger computational cost as $z$ has to be evolved due to its smoothenss term \cite{someone}.

@@

The results obtained from these benchmark underline the findings from the experiments with the class room sequences.
Again the non-local and region order adaptive regularizer perform pretty good overall.
The reason for the local order adaptive scoring so high in the sintel benchmark is the fact that the sintel benchmark consists mainly on fronto-parallel motion~\cite{sintel}.
For the KITTI benchmarks the local order adaptive regularizer yields worse results than the simple second order and other adaptive regularizers.
So even on benchmark data, it can be seen that order adaption is worthwhile as it can provide better results than comparable single order approaches.

>>>>

%% Abstract section.
\abstract{%
  In variational optic flow estimation, the flow field between two consecutive images of a sequence is estimated by minimizing an energy functional.
  Usually this functional uses a regularization term in order to avoid unreasonable kinds of flow fields and allow for a unique solution to the ill-posed problem.
  Often the regularization is formulated as a constraint in terms of vanishing flow derivative of either first or second order which makes an algorithm suitable for different kinds of motion to be estimated.

  This paper discusses the recent approach by Maurer~et~al. on adaptively selecting regularization order to allow for a flexible method that can solve typical first and second order flow problems equally well.
  This approach also overcomes framewise exclusive regularization order, which is desireable as fronto-parallel and affine motions may be present at the same time. 
} % end of abstract

@@

In computer vision, the field of optic flow deals with the estimation of a 2-dimensional flow field based on two consecutive frames of an image sequence.
This is useful for the detection and tracking of objects, e.g. in robotics~\cite{robotics}, or in video compression tasks~\cite{videocoding}.
Different methods for flow estimation exist, Barron~et~al. classified the different approaches into differential, matching, energy-based and phase-based methods~\cite{opticflowtechniques}.
The differential methods are more commonly known as variational methods as they rely on the calculus of variations.
Typically variational models use an energy functional consisting of a data term and a regularization term which are to be minimized.
The regularization term is used to overcome ambigous solutions to the optic flow problem by placing constraints on the flow field.
Commonly the regularization terms are either of first or second order which allows for different kinds of flow fields to evolve.
In the following the concept of variational flow estimation is recapitulated and the variational approach by Maurer, Stoll and Bruhn~\cite{daspaper}, which allows for adapting regularization order, is motivated and presented.

@@

Unfortunately this sophisticated scheme comes at a larger computational cost as $z$ has to be evolved due to its smoothenss term (compare~\cite{someone}).

@@

The results obtained from these benchmark underline the findings from the experiments with the class room sequences.
Again the non-local and region order adaptive regularizer perform pretty good overall.
The local order adaptive regularizer scores high in the sintel benchmark yields rather poor results in the KITTI benchmarks where the simple second order and other adaptive regularizers worked quite well.
So even on benchmark data, it can be seen that order adaption is worthwhile as it can provide better results than comparable single order approaches.
